---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# microperimetR

This package will help you work with microperimetry data.  
It is built for centervue's maia and compass devices. 

## Features: 
- Extracting data from MAIA raw (tgz) files becomes as easy as pie.
- Fully automated comparison of your visual field data with normdata from the literature. 
- microperimetR has functions for both location-dependent and location-independent visual field analysis. Because the normdata is interpolated for location-dependent analysis, any custom grid can be used for both types of analysis. 
- microperimetR also includes functions for some more or less common visualistaion of visual field data

## Example

This is a basic example which shows you how to import your visual field data and plot the (estimated) mean deviation for each included test:

```{r example, warning=FALSE}
# save the tgz files from MAIA into your R working directory 
# devtools::install_github(tjebo/microperimetR)
library(microperimetR)
testdata <- read_maia(folder = file.path(getwd(), "norm_raw"))
comparedat <- compare_norm(testdata)
plot_MD(comparedat)
```
